Kids Basic Mutual Exclusivity

### 2019-02-11 stats/kids_me_novel.Rmd
add first pass of me experiments

## importing data
files <- dir("~/Work/Spin/raw_data/kids/basic_me/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/Spin/raw_data/kids/basic_me/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,44,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

>>>>

## importing data
files <- dir("~/Work/Spin/raw_data/kids/me_novel/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/Spin/raw_data/kids/me_novel/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,44,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}
